### 2016-11-16 src/local.tex
going to sleep

To analyze the approximation ratio achieved by the local search algorithm consider an 
arbitrary but fixed optimal matching $M^* = \{s_1, \ldots, s_m\}$,
where $s_1, \ldots, s_m$ are the stars induced by the optimal solution.
Given the solution outputted by the local search algorithm,
we build the \emph{conflict graph} of the two solutions in which each node
represents a star from the optimal solution and edges exits between two nodes if
the local search solution has at least one edge that connects two stars, formally 
$G_\text{conflict} = (V, E)$ 
where $\{v_i : s_i \in M^* \}$ 
and $E = \{(v_i, v_j) : \exists (u,v) \in M \land u \in s_i, v \in s_j \}$.
Denote by $d^*_i$ the sum of the vertex degree of the optimal solution in $s_i$, 
and by $d_i$ the sum of the vertex degree of the local search solution in $s_i$.

\begin{figure}[h]
\centering
\input{fig-conflict}
\caption[]{
\label{fig:carpool}
A carpool matching example: 
\subref{subfloat:input} 
a directed graph with capacities on the vertices and weights on the edges. 
\subref{subfloat:output}
a feasible matching with total weight of 26.
$P$ is the set of blue vertices, and $D$ is the set of red, dashed vertices. 
}
\end{figure}

>>>>

To analyze the approximation ratio achieved by the local search algorithm consider an 
arbitrary but fixed optimal matching $M^* = \{s_1, \ldots, s_m\}$,
where $s_1, \ldots, s_m$ are the stars induced by the optimal solution.
Given the solution outputted by the local search algorithm,
we build the \emph{conflict graph} of the two solutions in which each node
represents a star from the optimal solution and edges exits between two nodes if
the local search solution has at least one edge that connects two stars, formally 
$G_\text{conflict} = (V, E)$ 
where $\{v_i : s_i \in M^* \}$ 
and $E = \{(v_i, v_j) : \exists (u,v) \in M \land u \in s_i, v \in s_j \}$.
Figure~\ref{fig:conflict} depicts this concept.
Denote by $d^*_i$ the sum of the vertex degree of the optimal solution in $s_i$, 
and by $d_i$ the sum of the vertex degree of the local search solution in $s_i$.

\begin{figure}[h]
\centering
\input{fig-conflict}
\caption[]{
\label{fig:conflict}
\subref{subfloat:input} 
An optimal matching depicted by the dashed red edges,
and another solution depicted by the solid green edges.  
\subref{subfloat:output}
The conflict graph, the upper left vertex corresponds 
to the star that contains the vertices a,b,c.
The numbers inside the vertices corresponds to $d_i$.   
}
\end{figure}
